Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
sld overview

\section{Aircraft EPS Overview}
\label{sec:overview}
Intro to aircraft EPS... explain the buses and generators.
Possibly show the diagram from the Honeywell patent.
Possibly show our ``cartoon" diagram of an EPS system.

@@

\section{Numerical Examples}
\label{sec:numerical-examples}

@@

Load Shedding Priority Table:
Load 1: 60,000W, least preferred to shed.
Load 2: 60,000W, second-least preferred to shed
Load 3: 40,000W, most preferred to shed

>>>>

\section{Aircraft EPS Overview}
\label{sec:overview}
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\columnwidth]{figures/eps.png}
  \caption{\textbf{Single Line Diagram of Aircraft Electrical Power System} Detailed model of the EPS system from the Honeywell Patent used
  in this paper.}
  \label{fig:sld}
\end{figure*}
Figure~\ref{fig:sld} shows a detailed Single Line Diagram (SLD) of an aircraft EPS. The diagram shows AC and DC generators connected to the engines
as well as auxiliary power sources (APUs). These generators and power sources are responsible for providing power to the many critical and non-critical
AC and DC loads as well as power conversion equipments. Buses are responsible for distributing power from the generators to the loads. Electrical switches
called contactors route power from the generators to the buses. Current, voltage, and contactor sensors are used to monitor the status of the system. A
typical EPS controller consists of Generator Control Units (GCUs) and Bus Power Control Unit (BPCU). The GCU is used to regulate the power output of the
the generators as well as isolate failed generators. The BPCU is used to control the contactors thus making it responsible for routing power from the
generators to the load.

@@

\section{Numerical Examples}
\label{sec:numerical-examples}
In the following numerical examples, we show how Hierarchical LMS harnesses the Optimizing LMS and LL-LMS to handle interesting load shedding situations and failure scenarios.
For simplicity, let each of these examples be limited to the loads in the left side bus.
Further, to keep the examples simple, we just look at sheddable loads powered by a generator with a power cap of 100,000W.
In practice, aircraft EPS typically have a mix of sheddable and nonsheddable loads.

@@

%\begin{table}[t]
%\caption{Optimizing LMS reduces load shedding compared to the LL-LMS load shedding policy.}
%\label{T:example-1}
%\centering
\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
60,000 & 1 (least preferred to shed) \\
60,000 & 2 (middle priority to shed) \\ 
40,000 & 3 (most preferred to shed) \\ \hline
\end{tabular}
%\end{table}
